### 2015-04-20 paper.tex
Change tense

The present task is to acquire a new dataset for the lower solidity RM2 turbine,
but at higher Reynolds numbers than those achieved in the experiments at SAFL.
It is also suspected that the strut drag model in CACTUS could be the source of
some discrepancy. The strut drag will be deliberately modified in the physical
model to provide data to help answer that question. This dataset will be
publicly available for both validation of CACTUS and other numerical models.
This report details the experimental test plan for acquiring, processing, and
archiving this data, which includes development of a scaled physical model, and
descriptions of the experimental setup and procedure to be performed in a towing
tank at the University of New Hampshire (UNH).

>>>>

The present task was to acquire a new dataset for the lower solidity RM2
turbine, but at higher Reynolds numbers than those achieved in the experiments
at SAFL. It is also suspected that the strut drag model in CACTUS could be the
source of some discrepancy. The strut drag was deliberately modified in the
physical model to provide data to help answer that question. This dataset is
publicly available for both validation of CACTUS and other numerical models.
